Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-03-20 pkg/disttree/inst/draft/draft.Rnw
work on Section 2
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2064 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 1b2913aa57cea1e52d9efe57cccf8e122c331578

%% packages
\usepackage{amstext}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{thumbpdf,lmodern}
%\usepackage{rotating}
%\usepackage{caption}
%\captionsetup{format=hang}
%\usepackage{subcaption}
\usepackage{Sweave}
%\usepackage{enumitem}
%\usepackage{graphicx}
\usepackage{array, makecell}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning,shapes,arrows,decorations.pathreplacing,calc,automata,mindmap}
%\usepackage[pagebackref=true]{hyperref}
%\usepackage{doi}

@@

\begin{document}
\SweaveOpts{concordance=TRUE}

\SweaveOpts{eps=FALSE, keep.source=TRUE, eval = TRUE}

\SweaveOpts{eval = TRUE}
\section{Introduction}

@@

As illustrated in Figure~\ref{Devel_parmod} a wide range of tools has been developed 
in the field of parametric modeling. Especially the shift from conditional mean 
regression models to distributional regression models has increased the application 
spectrum by allowing for much broader inference. In some cases further features 
such as the ability to capture non-additive effects or interactions are desirable 
which demands for more flexibility. Since tree-structured models provide these 
required features, combining them with parametric models can offer a framework 
that is able to deal with a wide variety of different modeling situations. 
In this section the novel methodology which embeds parametric modeling into 
the idea of tree-structured models will be introduced step by step. Starting 
with a simple distributional fit in Section~\ref{distfit} will be followed by 
building a distributional tree in Section~\ref{disttree} and finally a distributional 
forest in Section~\ref{distforest}.

\subsection{Distributional fit}
\label{distfit}
Fitting a distributional model to a set of observations without considering any 
covariates is a well known procedure which can for example be done by applying 
the maximum likelihood method. This is also the chosen approach in the methodology 
described in this section. 
%%% <TH> is is repeated on page 5, remove here </TH>

The goal is to fit a distributional model $\mathcal{D}(Y, \theta)$ to a response variable 
$Y \in \mathcal{Y}$ for a \textit{k}-dimensional vector of distribution parameters 
$\theta \in \Theta$ in case of a \textit{k}-parametric distribution. The distribution 
family with density function $f$ has to be specified in advance such that a 
log-likelihood function $\ell(\theta; Y) = \log(f(Y; \theta)$ is provided. Using 
the GAMLSS framework (\citealt{Rigby+Stasinopoulos:2005}) a wide range of distributions 
can be selected where each distribution parameter can be specified separately. 
This enables the model to deal with various features that can make the task of 
fitting a model very challenging such as censoring, truncation or heavy tails.

In our application of precipitation forecasting the response variable, which is 
the power transformed total precipitation amount within 24 hours, is expected 
to be normally distributed with mean/location parameter $\mu$ and standard 
deviation/scale parameter $\sigma$ and left-censored with censoring point 0. 
(The power transformation is used to remove large parts of the skewness of 
the data as further explained in Section~\ref{data}.) Therefore, the 
corresponding log-likelihood function with parameter vector 
$\theta = (\mu, \sigma)$ is
$$
\ell(\mu, \sigma; Y) = 
\begin{cases}
    \log\left(\frac{1}{\sigma} \cdot \phi\left(\frac{Y - \mu}{\sigma}\right) \right), & \text{if } Y > 0\\
    \vspace{0.1cm}
    \log\left(\Phi\left(\frac{-\mu}{\sigma}\right)\right), & \text{if } Y = 0
\end{cases}
$$
where $\phi$ and $\Phi$ are the probability density function and the 
distribution function of the standard normal distribution $\mathcal{N}(0,1)$. 
Next to the censored normal distribution also the censored logistic 
distribution is often chosen for the modeling of precipitation amounts. In 
\cite{Gebetsberger+Messner+Mayr:2017} this choice has been made in order 
to be able to deal with heavy tails which often appear in precipitation 
data. Another frequent application of probabilistic forecasting in meteorology 
is the modeling of near surface air temperature. In this case a normal 
distribution is often selected.

With the specification of the distribution family and its log-likelihood 
function the task of fitting a distributional model turns into the task 
of determining the distribution parameter~$\theta$. This is done by the 
following maximization based on a learning sample $\{y_i\}_{i=1,\ldots,n}$ 
of the response variable $Y$.
$$
\hat{\theta} = \max_{\theta \in \Theta} \sum_{i=1}^n \ell(\theta; y_i)
$$
which is equal to solving 
$$
\sum_{i=1}^n \frac{\partial \ell}{\partial \theta}(\hat{\theta}; y_i) = 0.
$$
In that way, a whole distribution is specified with all its features, 
including location, scale, and shape. However, fitting one global model 
to the whole data set might be too much of a generalization and therefore 
not represent the data and its features in a reasonable way. Moreover, 
if covariates are available it is desirable to include them into the model 
as they might provide important additional information. In our application 
on precipitation data a wide range of covariates is available from a numerical 
ensemble prediction system considering precipitation, temperature, sea level 
pressure and other meteorological quantities which might be of interest and 
have an influence on the predictions.

A common way of including these covariates is to consider them as regressors 
in a distributional model such that each parameter $\theta$ depends on covariates 
$\bold{Z} = (Z_1,\ldots,Z_m)$. This could for example be done by a linear function 
$g$. In that way the fitted model would be specified as 
$\mathcal{D}(Y, \theta = g(\bold{Z}))$. In order to avoid the restriction to linear 
effects one might also use a set of smooth functions $\{f_i\}_{i = 1,\ldots,p}$ 
to specify a more flexible model 
$\mathcal{D}(Y, \theta = f_1(\bold{Z}) + \ldots + f_p(\bold{Z}))$ applying a GAM structure. 
Another approach to distributional regression is proposed by 
\cite{Klein+Kneib+Lang:2015} where each parameter of a possibly complex 
distribution can be modeled by an additive term consisting of a variety of 
different functional effect types. These include non-linear effects, spatial 
effects, random coefficients and interaction surfaces which extends the 
flexibility compared to parametric models such as GAMLSS modeling only 
smooth effects.

A different approach on how to include covariates that also allows for 
non-additive effects and interactions is considered in the following. 
In particular, the covariates can be used to separate the data into more 
homogeneous subgroups. Doing so after fitting a global model to the whole 
data set (without considering any covariates) and then fitting a local 
model to each subgroup should improve the model remarkably. This 
procedure of splitting a data set into subgroups can be done by 
applying a tree algorithm.

\subsection{Distributional tree}
\label{disttree}
Given the fit of a global distributional model $\mathcal{D}(Y, \bold{\hat{\theta}})$, 
the idea is to use the information provided by this model together with a 
set of covariates $\bold{Z} = (Z_1, \ldots, Z_m) \in \mathcal{Z}$ 
to decide whether the data set should be split into subgroups or not. 
In particular, the information provided by the fitted model are the scores 
$$
s(\hat{\theta}, y_i) = \frac{\partial \ell}{\partial \theta}(\hat{\theta}; y_i).
$$ 
These values express how well the model fits the data regarding each 
parameter. Ideally they should fluctuate randomly around zero, 
similar to residuals in ordinary least squares estimation, but in 
this case there is a score value for each pair of estimated parameter 
$\hat{\theta}_j \in (\hat{\theta}_1, \ldots, \hat{\theta}_k) = \bold{\hat{\theta}}$ 
and observation $y_j \in \{y_i\}_{i = 1,\ldots, n}$. This enables the 
model to be sensitive to changes in each of the parameters which is one 
of the main advantages of distributional trees over other tree models 
considering only the mean of the distribution.

@@

For distributional trees a prediction for a (possibly new) set of covariates 
$\bold{z} = (z_1, \ldots, z_m)$ is made with the following strategy: 
All observations of the learning data set $\{(y_i,\bold{z}_i)\}_{i=1\ldots,n}$ 
which end up in the same terminal node of the tree as $\bold{z}$ are selected 
and a distributional model is fit on this subset. Selecting these observations
is done by including a weight vector 
$\bold{w}^{\text{tree}} = (w^{\text{tree}}_1, \ldots, w^{\text{tree}}_n)$ 
in the fitting process where
$$
w^{\text{tree}}_i(\bold{z}) = \sum_{b=1}^B I((\bold{z}_i \in \mathcal{B}_b) \land (\bold{z} \in \mathcal{B}_b)).
$$
The predicted distribution for $\bold{z}$ is then fully 
specified by the estimated parameter $\hat{\theta}(\bold{z})$ where
$$
\hat{\theta}(\bold{z}) = \max_{\theta \in \Theta} \sum_{i=1}^n w^{\text{tree}}_i(\bold{z}) \cdot \ell(\theta; y_i).
$$

@@

Forest models differ mainly in the way how the trees are combined to make predictions. 
Following the strategy explained and proposed by \cite{Hothorn+Zeileis:2017} we 
interpret random forests as adaptive local likelihood estimators as distributional 
models are fit locally in subgroups while the term ``adaptive'' refers to the 
dependence on the splitting variables $\bold{Z}$ and the resulting subgroups 
and weighing schemes. In this case the forest itself is only used to evaluate 
neighborhood relationships among the observations which can then be included 
in the fitting process. In transformation forests by \cite{Hothorn+Zeileis:2017} 
so-called ``nearest neighbor weights'' are calculated as a measure of distance 
between observations. This approach has also already been applied in several 
random forest-type methods such as in ``adaptive nearest neighbors'' by 
\cite{Lin+Jeon:2006}, in ``quantile regression forests''  by  \cite{Meinshausen:2006} 
and in ``bagging survival trees'' by \cite{Hothorn+Lausen+Benner:2004}. 
The idea of nearest neighbor weights is to measure similarity of a pair of 
observations by counting the number of trees in which it is asigned to the 
same terminal node.
%Similar observations have a high probability of ending up in the same terminal 
%node whereas this probability is low for quite different observations. 
%although the first random forest-type algorithm for the estimation of 
%conditional distribution functions was published more than a decade ago 
%(bagging survival trees, Hothorn et al. 2004). 
In particular, for a (possibly new) set of covariates 
$\bold{z} = (z_1, \ldots, z_m) $  such a set of weights 
$\bold{w}^{\text{forest}}~=~(w^{\text{forest}}_1, \ldots, w^{\text{forest}}_n)$ 
is obtained by the following procedure: For each tuple $(y_i,\bold{z}_i)$ in 
the learning data set $\{(y_i,\bold{z}_i)\}_{i=1\ldots,n}$ a weight is calculated 
by counting the number of trees in which $(y_i,\bold{z}_i)$ ends up in the same 
terminal node as $\bold{z}$:
$$
w^{\text{forest}}_i(\bold{z}) = \sum_{t=1}^T \sum_{b=1}^{B^t} I((\bold{z}_i \in \mathcal{B}^t_b) \land (\bold{z} \in \mathcal{B}^t_b))
$$
where $T$ is the number of trees of the forest, $B^t$ is the number of terminal 
nodes of the \textit{t}-th tree and $\mathcal{B}^t_b$ represents the \textit{b}-th 
terminal node of the \textit{t}-th tree.

Therefore, contrary to distributional trees, in distributional forests the whole 
learning data set can be used to fit a distributional model and specify the 
predicted distribution for a set of covariates. Compared to the formula for
predictions made by distributional trees the vector of tree weights 
$\bold{w}^{\text{tree}}$ containing only zeros and ones is now replaced by a 
vector of integer valued forest weights.
%%% <TH> we need references for the nearest neighbor weights, copy from
%%% "Transformation Forests" </TH>
%%%<TH> we need to cite "Transformation Forests" for the interpretation of
%%% random forests as adaptive local ML </TH>
This individual set of weights 
$\bold{w}^{\text{forest}}(\bold{z}) = (w^{\text{forest}}_1(\bold{z}), \ldots, w^{\text{forest}}_n(\bold{z}))$ 
for the set of covariates $\bold{z}$ can now be included in the 
estimation process of the distribution parameters and in that way leads 
to its individual parameter vector $\hat{\theta}(\bold{z})$ where
$$
\hat{\theta}(\bold{z}) =  \max_{\theta \in \Theta} \sum_{i=1}^n w^{\text{forest}}_i(\bold{z}) \cdot \ell(\theta; y_i)
$$
While in a distributional tree the same distribution is specified for all 
sets of covariates being in the same node, a distributional forest predicts 
and fits a different distribution for each different set of covariates due 
to the individual weights calculated separately for each set of covariates.

@@

\begin{itemize}
\item A distributional model $\mathcal{D}(Y, \theta)$ is fit to the set of 
observations $\{y_i\}_{i = 1,\ldots,n}$ by estimating the distribution 
parameter $\hat{\theta}$. This parameter can be a multidimensional 
vector $(\hat{\theta}_1, \ldots, \hat{\theta}_K)$, $K \in \mathbb{N}$, 
depending on the type of distribution. The estimation is done by 
maximizing the log-likelihood function $\ell(\theta; Y)$, i.e.
$$
\hat{\theta} = \max_{\theta \in \Theta} \sum_{i=1}^n \ell(\theta; y_i)
$$
which is equal to solving
$$
\sum_{i=1}^n s(\theta, y_i) = \sum_{i=1}^n \frac{\partial \ell}{\partial \theta}(\theta; y_i) = 0
$$
for $\theta$.

>>>>

%% packages
\usepackage{amstext,amsfonts,amsmath,bm,thumbpdf,lmodern}

%% tikz
\usepackage{array,makecell,tikz}
\usetikzlibrary{arrows.meta,positioning,shapes,arrows,decorations.pathreplacing,calc,automata,mindmap}

%% need no \usepackage{Sweave}
\SweaveOpts{concordance=FALSE, eps=FALSE, keep.source=TRUE, eval = TRUE}

@@

\begin{document}

\section{Introduction}

@@

To embed the distributional approach from GAMLSS into regression trees and random
forests, we proceed in three steps. (1)~To fix notation, we briefly review fitting
distributions using standard maximum likelihood in in Section~\ref{distfit}.
(2)~A recursive partitioning strategy based on the corresponding scores (or
gradients) is introduced in Section~\ref{disttree}, leading to distributional
trees. (3)~Ensembles of distributional trees fitted to randomized subsamples are
employed to establish distributional forests in Section~\ref{distforest}.

The general distributional notation is exemplified in all three steps for the
zero-censored Gaussian distribution. The latter is employed in the empirical
in the empirical case study in Section~\ref{ProbabilisticForecasting} to model
power-transformed daily precipitation amounts.

\subsection{Distributional fit}
\label{distfit}

A distributional model $\mathcal{D}(Y, \bm{\theta})$ is considered for the response
variable $Y \in \mathcal{Y}$ using the distributional family $\mathcal{D}$ with
\textit{k}-dimensional parameter vector $\bm{\theta} \in \bold{\Theta}$. Based on the
corresponding probability density function $f(Y; \bm{\theta})$ the log-likelihood
function is defined $\ell(\bm{\theta}; Y) = \log\{f(Y; \bm{\theta})\}$. The GAMLSS
framework \citep{Rigby+Stasinopoulos:2005} provides a wide range of such
distributional families with parameterizations corresponding to location, scale,
and shape. Furthermore, censoring and/or truncation of these distributions
can be incorporated in the usual straightforward way \fixme{reference needed}.

To capture both location and scale of the probabilistic precipitation forecasts
while accounting for a point mass at zero precipitation (i.e., dry days without
rain), zero-censored Gaussian distribution with with mean/location parameter
$\mu$ and standard deviation/scale parameter $\sigma$ is employed. Therefore,
the corresponding log-likelihood function with parameter vector 
$\bm{\theta} = (\mu, \sigma)$ is
$$
\ell(\mu, \sigma; Y) = 
\begin{cases}
    \log\left\{\frac{1}{\sigma} \cdot \phi\left(\frac{Y - \mu}{\sigma}\right) \right\}, & \text{if } Y > 0\\[0.2cm]
    \log\left\{\Phi\left(\frac{-\mu}{\sigma}\right)\right\}, & \text{if } Y = 0
\end{cases}
$$
where $\phi$ and $\Phi$ are the probability density function and the 
distribution function of the standard normal distribution $\mathcal{N}(0,1)$. 
Other distributions $\mathcal{D}$ and corresponding log-likelihoods
$\ell(\mu, \sigma; Y)$ could be set up in the same way, e.g., for
censored shifted gamma distributions \citep{Scheuerer+Hamill:2015} or
zero-censored logistic distributions \citep{Gebetsberger+Messner+Mayr:2017}.

With the specification of the distribution family and its log-likelihood 
function the task of fitting a distributional model turns into the task 
of estimating the distribution parameter~$\bm{\theta}$. This is commonly done by
maximum likelihood (ML) based on the learning sample
$\{y_i\}_{i = 1, \dots, n}$ of the response variable $Y$. The maximum
likelihood estimator (MLE) $\bm{\hat \theta}$ is given by
$$ \label{eq:mle}
\bm{\hat \theta} = \argmax_{\bm{\theta} \in \bold{\Theta}} \sum_{i=1}^n \ell(\bm{\theta}; y_i).
$$
Equivalently, this can be defined based on the corresponding first-order
conditions
$$ \label{eq:foc}
\sum_{i = 1}^n s(\bm{\hat \theta}, y_i) = 0,
$$
where $s(\bm{\theta}, y_i)$ is the associated score function
$$ \label{eq:score}
s(\bm{\theta}, y_i) = \frac{\partial \ell}{\partial \bm{\theta}}(\bm{\theta}; y_i).
$$ 
The latter is subsequently employed as a general goodness-of-fit measure
for individual observations $y_i$ and parameters $\bm{\theta}$.

\subsection{Distributional tree}
\label{disttree}

Typically, a single global model $\mathcal{D}(Y, \bm{\theta})$ is not sufficient
for reasonably representing the data and covariates $\bold{Z} = Z_1, \dots, Z_m \in \mathcal{Z}$ are
employed to capture differences in the distribution parameters $\bm{\theta}$.
In weather forecasting, these covariates typically include the output
from numerical weather prediction systems and/or lagged weather observations.

To incorporate the covariates into the distributional model, GAMLSS considers
them as regressors so that an additive predictor
$g_j(\theta_j) = f_{j,1}(\bold{Z}) + f_{j,2}(\bold{Z}) + \dots$
with link function $g_j(\cdot)$ is used for every parameter $\theta_j$
($j = 1, \dots, k$) based on smooth terms $f_{j,k}$ such as
nonlinear effects, spatial effects, random coefficients, or interaction surfaces
\citep{Klein+Kneib+Lang:2015}. However, this requires specifying the
additive terms and their functional forms in advance which is often difficult in
practice, especially if the number of covariates $m$ is large.

Regression trees generally take a different approach for automatically
including covariates in a data-driven way that also allows for abrupt
changes, non-additive effects, and interactions. In the context of
distributional models the goal is to partition the covariate space
$\mathcal{Z}$ recursively into disjoint segments so that a homogenous
distributional model for the response $Y$ can be found with segment-specific
parameters. More specifically, the $B$ disjoint segments $\mathcal{B}_b$
($b = 1, \dots, B$) partition the covariate space
$$ \label{eq:partition}
\mathcal{Z} = \dot{\bigcup\limits_{b = 1, \ldots, \textit{B}}} \mathcal{B}_b,
$$
and a local distributional model $\mathcal{D}(Y, \bm{theta}^(b))$
(i.e., with segment-specific parameters $\bm{theta}^(b)$) is fitted to the
response $Y$ in that segment.

To find the segments $\mathcal{B}_b$ that are (approximately) homogenous
with respect to the distributional model with given parameters, the idea
is to use a gradient-based recursive partitioning approach. In a given
subsample of the learning data this fits the model by ML (see
Equation~\ref{eq:mle}) and then assess the goodness of fit by looking at the
scores $s(\bm{\hat \theta}; y_i)$ (see Equation~\ref{eq:score}).

\fixme{still more to do}

These values express how well the model fits the data regarding each 
parameter. Ideally they should fluctuate randomly around zero, 
similar to residuals in ordinary least squares estimation, but in 
this case there is a score value for each pair of estimated parameter 
$\hat{\theta}_j \in (\hat{\theta}_1, \ldots, \hat{\theta}_k) = \bold{\hat{\theta}}$ 
and observation $y_j \in \{y_i\}_{i = 1,\ldots, n}$. This enables the 
model to be sensitive to changes in each of the parameters which is one 
of the main advantages of distributional trees over other tree models 
considering only the mean of the distribution.

@@

For distributional trees a prediction for a (possibly new) set of covariates 
$\bold{z} = (z_1, \ldots, z_m)$ is made with the following strategy: 
All observations of the learning data set $\{(y_i,\bold{z}_i)\}_{i=1\ldots,n}$ 
which end up in the same terminal node of the tree as $\bold{z}$ are selected 
and a distributional model is fit on this subset. Selecting these observations
is done by including a weight vector 
$\bold{w}^{\text{tree}} = (w^{\text{tree}}_1, \ldots, w^{\text{tree}}_n)$ 
in the fitting process where
$$
w^{\text{tree}}_i(\bold{z}) = \sum_{b=1}^B I((\bold{z}_i \in \mathcal{B}_b) \land (\bold{z} \in \mathcal{B}_b)).
$$
The predicted distribution for $\bold{z}$ is then fully 
specified by the estimated parameter $\hat{\theta}(\bold{z})$ where
$$
\hat{\theta}(\bold{z}) = \argmax_{\theta \in \Theta} \sum_{i=1}^n w^{\text{tree}}_i(\bold{z}) \cdot \ell(\theta; y_i).
$$

@@

Forest models differ mainly in the way how the trees are combined to make predictions. 
Following the strategy explained and proposed by \cite{Hothorn+Zeileis:2017} we 
interpret random forests as adaptive local likelihood estimators as distributional 
models are fit locally in subgroups while the term ``adaptive'' refers to the 
dependence on the splitting variables $\bold{Z}$ and the resulting subgroups 
and weighing schemes. In this case the forest itself is only used to evaluate 
neighborhood relationships among the observations which can then be included 
in the fitting process. In transformation forests by \cite{Hothorn+Zeileis:2017} 
so-called ``nearest neighbor weights'' are calculated as a measure of distance 
between observations. This approach has also already been applied in several 
random forest-type methods such as in ``adaptive nearest neighbors'' by 
\cite{Lin+Jeon:2006}, in ``quantile regression forests''  by  \cite{Meinshausen:2006} 
and in ``bagging survival trees'' by \cite{Hothorn+Lausen+Benner:2004}. 
The idea of nearest neighbor weights is to measure similarity of a pair of 
observations by counting the number of trees in which it is asigned to the 
same terminal node.
%Similar observations have a high probability of ending up in the same terminal 
%node whereas this probability is low for quite different observations. 
%although the first random forest-type algorithm for the estimation of 
%conditional distribution functions was published more than a decade ago 
%(bagging survival trees, Hothorn et al. 2004). 
In particular, for a (possibly new) set of covariates 
$\bold{z} = (z_1, \ldots, z_m) $  such a set of weights 
$\bold{w}^{\text{forest}}~=~(w^{\text{forest}}_1, \ldots, w^{\text{forest}}_n)$ 
is obtained by the following procedure: For each tuple $(y_i,\bold{z}_i)$ in 
the learning data set $\{(y_i,\bold{z}_i)\}_{i=1\ldots,n}$ a weight is calculated 
by counting the number of trees in which $(y_i,\bold{z}_i)$ ends up in the same 
terminal node as $\bold{z}$:
$$
w^{\text{forest}}_i(\bold{z}) = \frac{1}{T} \sum_{t=1}^T \sum_{b=1}^{B^t} I((\bold{z}_i \in \mathcal{B}^t_b) \land (\bold{z} \in \mathcal{B}^t_b))
$$
where $T$ is the number of trees of the forest, $B^t$ is the number of terminal 
nodes of the \textit{t}-th tree and $\mathcal{B}^t_b$ represents the \textit{b}-th 
terminal node of the \textit{t}-th tree.

Therefore, contrary to distributional trees, in distributional forests the whole 
learning data set can be used to fit a distributional model and specify the 
predicted distribution for a set of covariates. Compared to the formula for
predictions made by distributional trees the vector of tree weights 
$\bold{w}^{\text{tree}}$ containing only zeros and ones is now replaced by a 
vector of integer valued forest weights.
%%% <TH> we need references for the nearest neighbor weights, copy from
%%% "Transformation Forests" </TH>
%%%<TH> we need to cite "Transformation Forests" for the interpretation of
%%% random forests as adaptive local ML </TH>
This individual set of weights 
$\bold{w}^{\text{forest}}(\bold{z}) = (w^{\text{forest}}_1(\bold{z}), \ldots, w^{\text{forest}}_n(\bold{z}))$ 
for the set of covariates $\bold{z}$ can now be included in the 
estimation process of the distribution parameters and in that way leads 
to its individual parameter vector $\hat{\theta}(\bold{z})$ where
$$
\hat{\theta}(\bold{z}) =  \argmax_{\theta \in \Theta} \sum_{i=1}^n w^{\text{forest}}_i(\bold{z}) \cdot \ell(\theta; y_i)
$$
While in a distributional tree the same distribution is specified for all 
sets of covariates being in the same node, a distributional forest predicts 
and fits a different distribution for each different set of covariates due 
to the individual weights calculated separately for each set of covariates.

@@

\begin{itemize}
\item A distributional model $\mathcal{D}(Y, \theta)$ is fit to the set of 
observations $\{y_i\}_{i = 1,\ldots,n}$ by estimating the distribution 
parameter $\hat{\theta}$. This parameter can be a multidimensional 
vector $(\hat{\theta}_1, \ldots, \hat{\theta}_K)$, $K \in \mathbb{N}$, 
depending on the type of distribution. The estimation is done by 
maximizing the log-likelihood function $\ell(\theta; Y)$, i.e.
$$
\hat{\theta} = \argmax_{\theta \in \Theta} \sum_{i=1}^n \ell(\theta; y_i)
$$
which is equal to solving
$$
\sum_{i=1}^n s(\theta, y_i) = \sum_{i=1}^n \frac{\partial \ell}{\partial \theta}(\theta; y_i) = 0
$$
for $\theta$.
